Multi-fluids for Representing Sub-filter-scale Convection

### 2020-04-21 submit2/makeFigs/RCE_singleColumn.tex
Will's changes and Hilary's changes to figures

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

@@

\usepackage{babel}
\begin{document}
\setlength\tabcolsep{0.5pt}%
\begin{tabular}{ccccc}
$\sigma$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\multicolumn{5}{c}{Horizontal averages of the resolved RCE test case between $t=10^{5}\text{s}$
and $2\times10^{5}\text{s}$}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/sigmaMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/uniformTransfer_Pi4e3_w/0/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/bMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/wMean} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/hiRes_wide/timeMean_w/PMean}\tabularnewline
\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
$b_{ij}^{T}=b_{i}$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
versus resolved (dashed)}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P_1}\tabularnewline
\multicolumn{5}{c}{Single column (solid) with $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ and
$b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$, $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$
versus resolved (dashed)}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u_1} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P_1}\tabularnewline
\end{tabular}
\end{document}

>>>>

%% LyX 2.2.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,british,times]{article}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[pdftex,a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\pagestyle{empty}
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{calc}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}

@@

\usepackage{babel}
\begin{document}
\setlength\tabcolsep{0.5pt}%
\begin{tabular}{ccccc}
$\sigma_{1}$ & $\sigma S\ (\text{s}^{-1})$  & $b\ (\text{m}\ \text{s}^{-2})$ & $w\ (\text{m}\ \text{s}^{-1})$ & $P\ (\text{m}^{2}\text{s}^{-2})$\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=b_{i}$,
\hspace{6pt}  $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_w/100000/P}\tabularnewline
\multicolumn{5}{c}{%
\fbox{\begin{minipage}[t]{0.7\columnwidth}%
\begin{center}
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $b_{ij}^{T}=\frac{1}{2}\left(b_{i}+b_{j}\right)$,
\hspace{6pt} $\gamma=2\times10^{3}\text{m}^{2}\text{s}^{-1}$ 
\par\end{center}%
\end{minipage}}}\tabularnewline
\includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/sigma} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/massTransfer} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/b} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/u} & \includegraphics[scale=0.7]{/home/hilary/OpenFOAM/hilary-7/run/hilary/RCE/Boussinesq/singleColumn/divTransfer_Pi4e3_divSigmau_bT05_w/100000/P}\tabularnewline
\end{tabular}
\end{document}
